Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-11-15 doc/ms.tex
udpate discussion of Dessart models in text

\textbf{In Figure~\ref{fig:dessart} we compare photometric observations of \abc\ to the DD and PDD models presented in \citet{2014MNRAS.441..532D}.}

Qualitatively, the PDD models provide a better match to the observations of \abc\ than DD models. In particular, PDD models provide higher luminosities and faster rise times in the days after explosion, a more rapid evolution towards blue optical colors, and the formation of strong \ion{C}{2} lines that gradually disappear in the $\sim$week after explosion. Quantitatively, there are still some short comings of the models presented in \citet{2014MNRAS.441..532D}. In particular, the power-law index for the $g$-band rise is $\alpha \approx 3$ for each of the PDD models, which is significantly more steep than $\alpha = 0.98$, which we measure for \abc. The optical colors for \abc\ are blue from our first epoch $\sim$1.7\,d after explosion and remain approximately constant in the 10\,d after explosion, whereas the PDD models in \citet{2014MNRAS.441..532D} either exhibit distinct color evolution (i.e.\ are not constant) or are too red in the first few days after explosion. Nevertheless, the PDD models presented in \citet{2014MNRAS.441..532D} provide several attractive explanations for the unusual features in the early behavior of \abc, and it may be possible that small adjustments to the model (e.g., additional mixing of the radioactive material, adjustments in the explosion energy, etc.) can better match \abc.

>>>>

\textbf{In Figure~\ref{fig:dessart} we compare photometric
observations of \abc\ to the large-$^{56}$Ni yield DD and PDD
models presented in \citet{2014MNRAS.441..532D}. DD and PDD models
with $M_\mathrm{Ni}/M_\odot \la 0.7$ and 0.5, respectively, fail to
match the early luminosity and blue colors of \abc. The PDD models
provide a better match to the observations than the DD models. The
PDD models evolve more rapidly towards blue colors and provide a
better match to the $g$-band flux in the days after explosion.
Furthermore, unlike the DD models, the PDD models exhibit strong
\ion{C}{2} lines that gradually disappear in the $\sim$week after
explosion \citet{2014MNRAS.441..532D}. In detail, the early wiggles
in the \abc\ light curve are not matched by the PDD models, which
exhibit more smooth variations. Nevertheless, the PDD models
presented in \citet{2014MNRAS.441..532D} provide several attractive
explanations for the unusual features in the early behavior of
\abc, and small adjustments to the model (e.g., additional mixing
of the radioactive material, which \citeauthor{2014MNRAS.441..532D}
only explore for the DD model) may better match \abc. }
